


```{r setup, include=FALSE}

  # Load package
  pacman::p_load(
    fixest,
    modelsummary,
    margins,
    wooldridge,
    AER,
    janitor,
    kableExtra,
    tidyverse,
    haven,
    patchwork,
    ggplot2,
    jtools,
    lme4,
    psych,
    stringi,
    dplyr,
    corrplot, 
    stargazer,
    ggcorrplot,
    reshape2,
    DT,
    ggeffects,
    tinytex,
    alpaca
  )

library(htmltools)


```




# Load the dataset:

```{r, echo = T, eval=T}

# load data

 df <- read.csv("/.../data_5R_26May.csv")

```



## Split the dataset into two groups of move toward and move away:

```{r}

  df_p <- df %>% 
  filter( (peer_move_similarity > 0) &  (year_modified >= 2001) & (year_modified <= 2021))

  df_n <- df %>% 
  filter( (peer_move_similarity < 0) &  (year_modified >= 2001) & (year_modified <= 2021) )

```


# Summary: 
We run four regressions based on different datasets and different models. The first three are without the dummy variable of "move_toward." 
The first one includes the entire dataset. The second data contains those peers moving toward the focal firm, and the third is the opposite. 
The fourth model considers the dummy variable. 
In the end, I graph the moderation impacts, and common analysts and heterogeneity (homogeneity) could strongly change the slope sign. 

```{r}

df <- df %>% mutate(peer_move_similarity_move_away = peer_move_similarity * move_away)
df <- df %>% mutate(peer_move_similarity_move_toward = peer_move_similarity * move_toward)

df <- df %>% mutate(peer_move_similarity_move_away_t2 = peer_move_similarity_t2 * move_away_t2)
df <- df %>% mutate(peer_move_similarity_move_toward_t2 = peer_move_similarity_t2 * move_toward_t2)

df_2001 <- df %>% filter( (year_modified >= 2001) & (year_modified <= 2021) )


```



# Move_away:
```{r}

    # GVKEY.focal + GVKEY.peer

models <- list (
    
  "Model 1" = feols (focal_move_similarity ~ 
  roa_win_x + roa_rel +   log_at_win_x + log_at_rel_win + 
  slack_avail_win_x + slack_avail_win_y + 
  rd_intensity_win_x + rd_intensity_win_y + 
   meanrec_diff_90_previous_focal 	+ car3 + strategy_unique_peer + strategy_unique_focal + sales_growth_naicsh4_win_x + hhi_naicsh4_inv_win_x +
   similarity_f0_p0  + typicality_4_focal_t1   + typicality_4_focal_t2 + avg_change_size_3y_focal + 
  moving_toward_industry   | GVKEY.focal + year_modified , data= df_2001,  vcov = "hetero"),

   "Model 2" = feols (focal_move_similarity ~ car3 + sales_growth_naicsh4_win_x + 
  peer_move_similarity_move_away  	  + meanrec_diff_90_previous_focal  + hhi_naicsh4_inv_win_x + 
  +   rd_intensity_win_x + rd_intensity_win_y + typicality_4_focal_t1   + typicality_4_focal_t2 + avg_change_size_3y_focal + strategy_unique_peer + strategy_unique_focal + 
  log_at_win_x + log_at_rel_win + 
  slack_avail_win_x + slack_avail_win_y + roa_win_x + roa_rel + moving_toward_industry + 
  similarity_f0_p0   | GVKEY.focal + year_modified , data= df_2001, vcov = "hetero"
   ),
   
  "Model 3" = feols (focal_move_similarity ~ 
  peer_move_similarity_move_away  	  + meanrec_diff_90_previous_focal  + hhi_naicsh4_inv_win_x + sales_growth_naicsh4_win_x + 
    up_after_360 * peer_move_similarity_move_away + up_after_360 +  rd_intensity_win_x + rd_intensity_win_y + 
  log_at_win_x + log_at_rel_win + typicality_4_focal_t1    + typicality_4_focal_t2 + avg_change_size_3y_focal + strategy_unique_peer + strategy_unique_focal + 
  slack_avail_win_x + slack_avail_win_y + roa_win_x + roa_rel + moving_toward_industry + car3 + 
  similarity_f0_p0  | GVKEY.focal + year_modified , data= df_2001, vcov = "hetero"
   ),

      "Model 4" = feols (focal_move_similarity ~ car3 + 
  peer_move_similarity_move_away   + meanrec_diff_90_previous_focal  +  hhi_naicsh4_inv_win_x + sales_growth_naicsh4_win_x + 
    analysts_peer_number * peer_move_similarity_move_away + analysts_peer_number  +   rd_intensity_win_x + rd_intensity_win_y + 
  log_at_win_x + log_at_rel_win + typicality_4_focal_t1    + typicality_4_focal_t2 + avg_change_size_3y_focal + strategy_unique_peer + strategy_unique_focal + 
  slack_avail_win_x + slack_avail_win_y + roa_win_x + roa_rel + moving_toward_industry + 
  similarity_f0_p0   | GVKEY.focal + year_modified , data= df_2001, vcov = "hetero"
   ),
  
   "Model 5" = feols (focal_move_similarity ~ car3 + 
  peer_move_similarity_move_away	 	  + meanrec_diff_90_previous_focal   + hhi_naicsh4_inv_win_x + sales_growth_naicsh4_win_x + 
     rd_intensity_win_x + rd_intensity_win_y + common_analysts_focal + typicality_4_focal_t1   + typicality_4_focal_t2 + avg_change_size_3y_focal + strategy_unique_peer + strategy_unique_focal + 
  log_at_win_x + log_at_rel_win + common_analysts_focal * peer_move_similarity_move_away  + 
  slack_avail_win_x + slack_avail_win_y + roa_win_x + roa_rel + moving_toward_industry + 
  similarity_f0_p0  | GVKEY.focal + year_modified , data= df_2001, vcov = "hetero"
   ),  

   "Model 6" = feols (focal_move_similarity ~  car3 + sales_growth_naicsh4_win_x + 
   peer_move_similarity_move_away 	  + meanrec_diff_90_previous_focal+ 
        peer_move_similarity_move_away * up_after_360  + typicality_4_focal_t1   + typicality_4_focal_t2 + avg_change_size_3y_focal + strategy_unique_peer + strategy_unique_focal + 
  common_analysts_focal * peer_move_similarity_move_away   + 
  peer_move_similarity_move_away * analysts_peer_number + 
  analysts_peer_number + up_after_360 + 
  log_at_win_x + log_at_rel_win + hhi_naicsh4_inv_win_x + 
  slack_avail_win_x + slack_avail_win_y  + roa_rel + common_analysts_focal +   

   + similarity_f0_p0 + roa_win_x +  
     moving_toward_industry 
    + rd_intensity_win_x + rd_intensity_win_y  | GVKEY.focal + year_modified , data= df_2001,  vcov = "hetero"
   )

)


mean(df_2001$common_analysts_focal, na.rm = TRUE)


sd(df_2001$common_analysts_focal, na.rm = TRUE)



number_of_unique_gvkey_focal <- df_2001 %>%
  dplyr::summarise(n_distinct(GVKEY.focal))

# To print the number
print(number_of_unique_gvkey_focal)

 variable_order <- c(
  "^Rival move away$",
  "Recommendation upgrades of rival's move",
  "Sum",
  "Rival analyst coverage" ,
  "Analyst overlap"
)



etable_result1 <- etable(models,
order = variable_order,
  dict = c(
    slack_avail_win_x = "Focal firm slack",
    peer_move_similarity_move_toward = "Rival move toward",
    focal_move_similarity_lagged = "Focal firm move lagged",
    meanrec_diff_90_previous_focal = "Focal firm mean recom change",
    peer_move_similarity_move_away = "Rival move away",
    forecast_dispersion_focal = "Focal firm forecast dispersion",
    log_at_win_x = "Focal firm total assets",
    log_at_rel_win = "Relative total assets",
    slack_avail_win_y = "Rival firm slack",
    roa_win_x = "Focal firm ROA",
    roa_rel = "Relative ROA",
    moving_toward_industry = "Focal firm movement toward trends",
    similarity_f0_p0 = "Initial strategic similarity t0",
    rd_intensity_win_x = "Focal firm R&D intensity",
    rd_intensity_win_y = "Rival firm R&D intensity",
    common_analysts_focal = "Analyst overlap",
    up_after_360 = "Recommendation upgrades of rival's move (yearly)",
    up_after_90 = "Recommendation upgrades of rival's move (quarterly)",
    analysts_peer_number = "Rival analyst coverage",
    `peer_move_similarity_move_away x up_after_360` = "Rival move away*Recommendation upgrades of rival's move",
    `peer_move_similarity_move_away x common_analysts_focal` = "Rival move away*Analyst overlap",
    `peer_move_similarity_move_away x analysts_peer_number` = "Rival move away*Rival analysts coverage",
    focal_move_similarity = "Focal firm repositioning", 
    mergers_win_x = "Focal firm mergers expenditures",
    GVKEY.focal	= "Focal firm", 
    year_modified = "Year",
    typicality_4_focal_t1= "Focal firm typicality t1", 
    typicality_4_focal_t2= "Focal firm typicality t2", 
    typicality_4_peer_t1 = "Peer firm typicality",
    avg_change_size_3y_focal = 'Focal firm change size average in the past three years', 
    strategy_unique_peer = 'Rival strategy uniqueness',
    strategy_unique_focal = 'Focal firm strategy uniqueness', 
    recom_update = 'Sum of recommendation',
    car3 = 'Rival firm abnormal return',
    sales_growth_naicsh4_win_x = 'Focal firm industry sales growth' ,
    sales_growth_naicsh4_y = 'Rival firm industry sales growth',
    hhi_naicsh4_inv_win_x = 'Focal firm industry competition (1-hhi)',
    rd_10_win = "R&D intensity 10",
    rd_15_win = "R&D intensity 15",
    rd_intensity_industry_6 = "R&D intensity 6 focal"
  ),
  digits= "r3",
   vcov = "hetero")  %>%
  kbl() %>%
  kable_classic_2(html_font = "Cambria", full_width = FALSE) %>%
  footnote(general = "Significance levels: *p<0.05, **p<0.01, ***p<0.001", 
           general_title = "Note: ")


etable_result1

 
```




# 2) move_toward with robustness controls:

```{r}


  models1 <- list (

  "Model 7" = feols (focal_move_similarity ~ 
  roa_win_x + roa_rel +   log_at_win_x + log_at_rel_win + 
  slack_avail_win_x + slack_avail_win_y + 
  rd_intensity_win_x + rd_intensity_win_y + 
   meanrec_diff_90_previous_focal 	+ car3 + strategy_unique_peer + strategy_unique_focal + sales_growth_naicsh4_win_x + hhi_naicsh4_inv_win_x +
   similarity_f0_p0  + typicality_4_focal_t1   + typicality_4_focal_t2 + avg_change_size_3y_focal + 
  moving_toward_industry  | GVKEY.focal + year_modified , data= df_2001, vcov= 'hetero'),
  
  "Model 8" = feols (focal_move_similarity ~  car3 + sales_growth_naicsh4_win_x +
  peer_move_similarity_move_toward 	  +  meanrec_diff_90_previous_focal   + typicality_4_focal_t1    + typicality_4_focal_t2 + 
  avg_change_size_3y_focal + strategy_unique_peer + strategy_unique_focal  + hhi_naicsh4_inv_win_x  + 
  log_at_win_x + log_at_rel_win + slack_avail_win_x + slack_avail_win_y + roa_win_x + roa_rel + moving_toward_industry 
  + similarity_f0_p0 +  rd_intensity_win_x + rd_intensity_win_y +  focal_move_similarity_lagged  | GVKEY.focal + year_modified , data= df_2001, vcov= 'hetero'),

    "Model 9" = feols (focal_move_similarity ~ car3 + peer_move_similarity_move_toward  + meanrec_diff_90_previous_focal  + 
  rd_5_win + rd_5_win * peer_move_similarity_move_toward  +  hhi_naicsh4_inv_win_x  + 
  log_at_win_x + log_at_rel_win  + typicality_4_focal_t1    + typicality_4_focal_t2 + avg_change_size_3y_focal + strategy_unique_peer + strategy_unique_focal + 
  slack_avail_win_x + slack_avail_win_y + roa_win_x + roa_rel + moving_toward_industry
   + similarity_f0_p0 + rd_intensity_win_x + rd_intensity_win_y +  focal_move_similarity_lagged  | GVKEY.focal + year_modified , data= df_2001,  vcov = "hetero"
   ),

   "Model 10" = feols (focal_move_similarity ~ car3  +  sales_growth_naicsh4_win_x +
  peer_move_similarity_move_toward	  + meanrec_diff_90_previous_focal + 
  common_analysts_focal +   rd_intensity_win_x + rd_intensity_win_y  + typicality_4_focal_t1    + typicality_4_focal_t2 + 
  avg_change_size_3y_focal + strategy_unique_peer + strategy_unique_focal +  hhi_naicsh4_inv_win_x  + 
  log_at_win_x + log_at_rel_win + common_analysts_focal * peer_move_similarity_move_toward +
  slack_avail_win_x + slack_avail_win_y + roa_win_x + roa_rel + moving_toward_industry + 
  similarity_f0_p0 +  focal_move_similarity_lagged | GVKEY.focal + year_modified , data= df_2001, vcov= 'hetero'
   ),

   "Model 11" = feols (focal_move_similarity ~ car3  +  sales_growth_naicsh4_win_x +
   peer_move_similarity_move_toward	  +  meanrec_diff_90_previous_focal  +  hhi_naicsh4_inv_win_x  + 
   rd_intensity_win_y + typicality_4_focal_t1    + typicality_4_focal_t2 + avg_change_size_3y_focal + strategy_unique_peer + strategy_unique_focal + 
  log_at_win_x + log_at_rel_win  +   rd_5_win + rd_5_win * peer_move_similarity_move_toward + 
  slack_avail_win_x + slack_avail_win_y  + roa_rel + common_analysts_focal +   
  common_analysts_focal * peer_move_similarity_move_toward  +
   similarity_f0_p0  + 
   roa_win_x + 
     moving_toward_industry
    + rd_intensity_win_x +  focal_move_similarity_lagged  | GVKEY.focal + year_modified  , data= df_2001,
    vcov= 'hetero'
   )

)


variable_order <- c(
  "^Rival move toward$",
  "R&D intensity of the environment",
  'Rival firm industry competition',
  'Rival firm industry homogeneity',
  'Focal firm industry homogeneity',
  "Analyst overlap"
)


etable_result <- etable(models1,
order = variable_order,
  dict = c(
    slack_avail_win_x = "Focal firm slack",
    focal_move_similarity_lagged = "Focal firm move lagged",
    peer_move_similarity_move_toward = "Rival move toward",
    log_at_win_x = "Focal firm total assets",
    log_at_rel_win = "Relative total assets",
    slack_avail_win_y = "Rival firm slack",
    meanrec_diff_90_previous_focal= "Focal firm mean recom change",
    roa_win_x = "Focal firm ROA",
    roa_rel = "Relative ROA",
    moving_toward_industry = "Focal firm movement toward trends",
    similarity_f0_p0 = "Initial strategic similarity t0",
    rd_intensity_win_x = "Focal firm R&D intensity",
    rd_intensity_win_y = "Rival R&D intensity",
    common_analysts_focal = "Analyst overlap",
    rd_5_win = "R&D intensity of the environment",
    rd_10_win = "R&D intensity of the environment",
    `Rival move toward x Common analysts` = "Rival move toward*Analyst overlap",
    `Rival move toward x rd_5` = "Rival move toward*R&D intensity of the environment",
      mergers_win_x = "Focal firm mergers expenditures",
    focal_move_similarity = "Focal firm repositioning", 
    GVKEY.focal	= "Focal firm", 
    year_modified = "Year",
    typicality_4_focal_t1= "Focal firm typicality t1", 
    typicality_4_focal_t2= "Focal firm typicality t2", 
    typicality_4_peer_t1= "Peer firm typicality", 
    avg_change_size_3y_focal = 'Focal firm change size average in the past three years', 
    strategy_unique_peer = 'Rival strategy uniqueness',
    strategy_unique_focal = 'Focal firm strategy uniqueness', 
    recom_update = 'Sum of recommendation',
    car3 = 'Rival firm abnormal return',
    sales_growth_naicsh4_win_x = 'Focal firm industry sales growth' ,
    sales_growth_naicsh4_y = 'Rival firm industry sales growth',
    hhi_naicsh4_inv_win_y = 'Rival firm industry competition (1-hhi)',
    hetero_naicsh4_peer= 'Rival firm industry heterogeneity',
    hhi_naicsh4_inv_win_x = 'Focal firm industry competition (1-hhi)',
    homogeneity_sumsim_naicsh4_focal = 'Focal firm industry homogeneity'
  ),
  digits= "r3",
  vcov = "hetero") %>%
 kbl() %>%
  kable_classic_2(
    html_font = "Cambria",
    full_width = F
  )%>%
footnote(general = "Significance levels: *p<0.05, **p<0.01, ***p<0.001", 
         general_title = "Note: ")



etable_result


```


  



############ PLOT ############
############ PLOT ############
############ PLOT ############
############ PLOT ############
############ PLOT ############
############ PLOT ############

```{r}


generate_plot_away_meanSDD <- function(df, moderation_var, moderation_var_name) {
  
  # Define range for peer_move_similarity
  peer_range <- seq(min(df$peer_move_similarity_move_away, na.rm = TRUE), 
                    max(df$peer_move_similarity_move_away, na.rm = TRUE), length.out = 1000)
  
  # Prepare prediction data template
  prediction_data <- data.frame(peer_move_similarity_move_away = peer_range)
  
  # Calculate mean and standard deviation for the moderation variable
  moderation_mean <- mean(df[[moderation_var]], na.rm = TRUE)
  moderation_sd <- sd(df[[moderation_var]], na.rm = TRUE)

  # Define levels for moderation variable based on mean and SD
  moderation_levels <- c("Average" = moderation_mean, 
                         "Low" = max(moderation_mean - moderation_sd, 0), 
                         "High" = moderation_mean + moderation_sd)



  # Set control variables to their means
  control_vars <- c( "meanrec_diff_90_previous_focal", 
                    "log_at_win_x", "log_at_rel_win", "slack_avail_win_x", "slack_avail_win_y",
                    "roa_win_x", "roa_rel", "moving_toward_industry", "similarity_f0_p0", 
                    "rd_intensity_win_x", "rd_intensity_win_y", "car3", "strategy_unique_peer" , "strategy_unique_focal" , 
                    "hhi_naicsh4_inv_win_x", "typicality_4_focal_t1", "typicality_4_focal_t2" , "avg_change_size_3y_focal", "sales_growth_naicsh4_win_x")


  for (var in control_vars) {
      prediction_data[[var]] <- mean(df[[var]], na.rm = TRUE)
  }
  
  # Set levels for fixed effects
  common_level_GVKEY_focal <- as.numeric(names(sort(table(df$GVKEY.focal), decreasing = TRUE)[1]))
  common_year_modified <- as.numeric(names(sort(table(df$year_modified), decreasing = TRUE)[1]))
  
  prediction_data$GVKEY.focal <- common_level_GVKEY_focal
  prediction_data$year_modified <- common_year_modified
  
  # Create the formula dynamically based on the input moderation variable
  formula_string <- paste0("focal_move_similarity ~ peer_move_similarity_move_away + meanrec_diff_90_previous_focal + ", 
                           moderation_var, " + ", moderation_var, " * peer_move_similarity_move_away + log_at_win_x + log_at_rel_win + slack_avail_win_x + 
                           slack_avail_win_y + roa_win_x + roa_rel + moving_toward_industry + similarity_f0_p0 + 
                           rd_intensity_win_x + rd_intensity_win_y + car3 + strategy_unique_peer + strategy_unique_focal + hhi_naicsh4_inv_win_x +
                           sales_growth_naicsh4_win_x +
                     typicality_4_focal_t1 + typicality_4_focal_t2 + avg_change_size_3y_focal | GVKEY.focal + year_modified")

  formula_obj <- as.formula(formula_string)
  
  # Model
  model <- feols(formula_obj, data = df, vcov = "hetero")
  
  # Predictions and slopes for different levels
  prediction_dfs <- list()
  slopes <- numeric(length(moderation_levels))
  
  for(level in names(moderation_levels)) {
    current_data <- prediction_data
    current_data[[moderation_var]] <- moderation_levels[level]
    current_data$predicted <- predict(model, newdata = current_data)
    current_data$Level <- level
    prediction_dfs[[level]] <- current_data

    # Choose two points to calculate the slope
    point1 <- current_data[1, ]
    point2 <- current_data[nrow(current_data), ]
    slope <- (point2$predicted - point1$predicted) / (point2$peer_move_similarity_move_away - point1$peer_move_similarity_move_away)
    slopes[level] <- slope
  }
  
  all_predictions <- do.call(rbind, prediction_dfs)
  
  # Output slopes
  slope_output <- setNames(slopes, names(moderation_levels))
  cat("Slopes for each level of '", moderation_var_name, "':\n")
  print(slope_output)


  # Plot
plot <- ggplot(all_predictions, aes(x = peer_move_similarity_move_away, y = predicted, color = Level)) +
    geom_line() +
    labs(y = "Focal firm repositioning", 
         x = "Rival move away",
         title = paste0("Moderation Effect of ", moderation_var_name),
         color = paste0("Level of ", moderation_var_name)) +
    theme_minimal() +
    theme(plot.title = element_text(size = 24), 
          axis.title = element_text(size = 18),
          axis.text = element_text(size = 14),  # Adjust the size of the axis tick labels
          legend.title = element_text(size = 16),
          legend.text = element_text(size = 14))

  
  list(plot = plot, slopes = slope_output)
  ggsave("my_plot2.pdf", plot, width = 9, height = 7.5)

}



```




```{r}


generate_plot_toward_meanSDD <- function(df, moderation_var, moderation_var_name) {
  
  # Define range for peer_move_similarity
  peer_range <- seq(min(df$peer_move_similarity_move_toward, na.rm = TRUE), 
                    max(df$peer_move_similarity_move_toward, na.rm = TRUE), length.out = 1000)
  
  # Prepare prediction data template
  prediction_data <- data.frame(peer_move_similarity_move_toward = peer_range)
  
  # Calculate mean and standard deviation for the moderation variable
  moderation_mean <- mean(df[[moderation_var]], na.rm = TRUE)
  moderation_sd <- sd(df[[moderation_var]], na.rm = TRUE)

  # Define levels for moderation variable based on mean and SD
  moderation_levels <- c("Average" = moderation_mean, 
                         "Low" = max(moderation_mean - moderation_sd, 0), 
                         "High" = moderation_mean + moderation_sd)

  # Set control variables to their means
  control_vars <- c( "meanrec_diff_90_previous_focal", 
                    "log_at_win_x", "log_at_rel_win", "slack_avail_win_x", "slack_avail_win_y",
                    "roa_win_x", "roa_rel", "moving_toward_industry", "similarity_f0_p0", 
                    "rd_intensity_win_x", "rd_intensity_win_y", "car3", 'strategy_unique_peer', 'strategy_unique_focal', 
                    'hhi_naicsh4_inv_win_x', 'typicality_4_focal_t1', 'typicality_4_focal_t2','avg_change_size_3y_focal', 'sales_growth_naicsh4_win_x')

  for (var in control_vars) {
      prediction_data[[var]] <- mean(df[[var]], na.rm = TRUE)
  }
  
  # Set levels for fixed effects
  common_level_GVKEY_focal <- as.numeric(names(sort(table(df$GVKEY.focal), decreasing = TRUE)[1]))
  common_year_modified <- as.numeric(names(sort(table(df$year_modified), decreasing = TRUE)[1]))
  
  prediction_data$GVKEY.focal <- common_level_GVKEY_focal
  prediction_data$year_modified <- common_year_modified
  
  # Create the formula dynamically based on the input moderation variable
  formula_string <- paste0("focal_move_similarity ~ peer_move_similarity_move_toward + ", 
                           moderation_var, " + ", moderation_var, " * peer_move_similarity_move_toward + meanrec_diff_90_previous_focal + 
                           log_at_win_x + log_at_rel_win + slack_avail_win_x + 
                           slack_avail_win_y + roa_win_x + roa_rel + moving_toward_industry + similarity_f0_p0  +
                           rd_intensity_win_x + rd_intensity_win_y + car3 + strategy_unique_peer + strategy_unique_focal + sales_growth_naicsh4_win_x + 
                    hhi_naicsh4_inv_win_x + typicality_4_focal_t1 + typicality_4_focal_t2 + avg_change_size_3y_focal | GVKEY.focal + year_modified")
 
  formula_obj <- as.formula(formula_string)
  
  # Model
  model <- feols(formula_obj, data = df, vcov = "hetero")
  
  # Predictions and slopes for different levels
  prediction_dfs <- list()
  slopes <- numeric(length(moderation_levels))
  
  for(level in names(moderation_levels)) {
    current_data <- prediction_data
    current_data[[moderation_var]] <- moderation_levels[level]
    current_data$predicted <- predict(model, newdata = current_data)
    current_data$Level <- level
    prediction_dfs[[level]] <- current_data

    # Choose two points to calculate the slope
    point1 <- current_data[1, ]
    point2 <- current_data[nrow(current_data), ]
    slope <- (point2$predicted - point1$predicted) / (point2$peer_move_similarity_move_toward - point1$peer_move_similarity_move_toward)
    slopes[level] <- slope
  }
  
  all_predictions <- do.call(rbind, prediction_dfs)
  
  # Output slopes
  slope_output <- setNames(slopes, names(moderation_levels))

  cat("Slopes for each level of '", moderation_var_name, "':\n")
  print(slope_output)


  # Plot
plot <- ggplot(all_predictions, aes(x = peer_move_similarity_move_toward, y = predicted, color = Level)) +
    geom_line() +
    labs(y = "Focal firm repositioning", 
         x = "Rival move toward",
         title = paste0("Moderation Effect of ", moderation_var_name),
         color = paste0("Level of ", moderation_var_name)) +
    theme_minimal() +
    theme(plot.title = element_text(size = 24), 
          axis.title = element_text(size = 18),
          axis.text = element_text(size = 14),  # Adjust the size of the axis tick labels
          legend.title = element_text(size = 16),
          legend.text = element_text(size = 14))
  
  list(plot = plot, slopes = slope_output)

ggsave("my_plot.pdf", plot, width = 9, height = 7.5)

}


```


```{r}
# My plot 2 for move away
# My plot 1 for move toward

# Move_away plots

generate_plot_away_meanSDD (df_2001, "up_after_360", "Recommendation upgrade of a rival's move")

generate_plot_away_meanSDD (df_2001, "common_analysts_focal", "Analyst overlap")

generate_plot_away_meanSDD (df_2001, "analysts_peer_number", "Analyst coverage of rival")


# Move_toward plots

generate_plot_toward_meanSDD (df_2001, "rd_5_win", "R&D intensity of the environment")

generate_plot_toward_meanSDD (df_2001, "common_analysts_focal", "Analyst overlap")

```


